User Preferences in Graphical and Textual Interfaces for Kubernetes

### 2021-08-25 Draft.tex
added some regex patterns

\subsubsection{Disruption}
We kept track of the patterns of switching between different inputs (composed as regular expressions) as a measure of disruption due to the number of times the participant had to task switch (for example, between typing and mousing) to complete the task. Tables \text{\ref{table:t6}--\ref{table:t9}} provide a list of the regular expressions participants used to complete the task with each tool.

@@

Three participants ranked the kubctl CLI as the tool interface they preferred to use to complete the task and one participant preferred the OpenShift console to complete the task.

@@

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  Recommendations & kubectl CLI & OpenShift Console \\ 
  \hline
  P1 &  &  \\ 
  \hline
  P2 & & \\
  \hline
  P3 & seems to be doing what it is supposed to do - minor problems can be super annoying though like this one: \href{https://github.com/kubernetes/kubernetes/issues/42552} & more scripting and automation? plugins? \\
  \hline
  P4 & better documentation & NA (not using it) \\
  \hline
  \end{tabular}
 \caption{Participant recommendations for improving tools.}
 \label{table:t10}
\end{table}

@@

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P1 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P1 regular expression patterns.}
 \label{table:t6}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P2 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P2 regular expression patterns.}
 \label{table:t7}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P3 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P3 regular expression patterns.}
 \label{table:t8}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P4 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P4 regular expression patterns.}
 \label{table:t9}
\end{table}

>>>>

\subsubsection{Disruption}
We kept track of the patterns of switching between different inputs (composed as regular expressions) as a measure of disruption due to the number of times the participant had to switch modalities (for example, between typing and mousing) to complete the task. Tables \text{\ref{table:t6}--\ref{table:t9}} provide a list of the regular expressions participants used to complete the task with each tool.

@@

All four participants ranked the kubctl CLI as the tool interface they preferred to use to complete the task.

@@

\begin{table}
 \centering
  \begin{tabular}{ | m{3cm} | m{6cm} | m{6cm} | } 
  \hline
  Recommendations & kubectl CLI & OpenShift Console \\ 
  \hline
  P1 & Cryptic syntax for many commands, hard to do easy things like switch contexts & More developer focused tools \\ 
  \hline
  P2 & & \\
  \hline
  P3 & Seems to be doing what it is supposed to do. Minor problems can be super annoying though like this one: \url{https://github.com/kubernetes/kubernetes/issues/42552} & More scripting and automation? Plugins? \\
  \hline
  P4 & Better documentation & NA (not using it) \\
  \hline
  \end{tabular}
 \caption{Participant recommendations for improving tools.}
 \label{table:t10}
\end{table}

@@

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P1 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution & KK & KMC \\ 
  \hline
  Copy/Paste &MMCMMKK & - \\
  \hline
  Navigation & M & MC \\
  \hline
  Tab Completion & - & - \\
  \hline
  \end{tabular}
 \caption{P1 regular expression patterns.}
 \label{table:t6}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P2 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution & KK & KMC \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & MC \\
  \hline
  Tab Completion & KKK & - \\
  \hline
  \end{tabular}
 \caption{P2 regular expression patterns.}
 \label{table:t7}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P3 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution & KK &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & MC \\
  \hline
  Tab Completion & & - \\
  \hline
  \end{tabular}
 \caption{P3 regular expression patterns.}
 \label{table:t8}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P4 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution & KK &  \\ 
  \hline
  Copy/Paste &  & \\
  \hline
  Navigation & & MC \\
  \hline
  Tab Completion & & - \\
  \hline
  \end{tabular}
 \caption{P4 regular expression patterns.}
 \label{table:t9}
\end{table}
